An Extensible Approach to Verification of Embedded Network Systems*

### 2014-04-25 tech-project/implementation.tex
added the smith reference back in and added the relationship diagram.

% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE... AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE. BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
\section{Implementation}
Development of our C translation tool can be logically partitioned into three distinct pieces: 
\begin{enumerate}
\item Arriving at a translation model (or, strategy) for an efficient, reliable C representation of RESOLVE.
\item Implementing reusable mechanisms for carrying out the C code generation process.
\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
\end{enumerate}
In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.

@@

@@

The relationship between the RESOLVE module type and c code generated is depicted at a high level in Figure \#. Unsurprisingly, concepts are represented in C by a single header \texttt{.h}. Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE. Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept. RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.

>>>>

% IN THIS SECTION SHOW SOME OF OUR TRANSLATED CODE... AND WALK THROUGH IT THE SAME WAY YOU DID WITH THE CONCEPT IN RESOLVE. BUT BEFORE YOU DO THAT, SHOW THE PICTURE (The one thats already here showing high level relationships and update it!).
\section{Implementation}
Development of our C translation tool can be logically partitioned into three distinct pieces: 
\begin{enumerate}
\item Arriving at a translation model (or, strategy) for a relatively efficient, accurate C representation of RESOLVE.
\item Implementing reusable mechanisms for carrying out the C code generation process.
\item Creation of a memory manager capable of safely allocating and freeing dynamic memory required by the generated code.
\end{enumerate}
In this section we discuss each of these phases using the LED component developed in Section \ref{sec:specifiying}.

@@

The relationship between the RESOLVE module type and C code generated by our tools depicted at a high level in Figure \ref{fig:relationship}.

\begin{figure}
\begin{center}
\includegraphics[scale=.55]{figs/relationship.pdf}
\end{center}
\caption{Native RESOLVE module files (left) and C files each produces (right).}
\label{fig:relationship}
\end{figure}

Unsurprisingly, concepts are represented in C by a single header \texttt{.h}. Some realizations connected to concepts are \texttt{externally} realized, denoting that they are not generated from RESOLVE. Additionally concepts can be \texttt{enhanced by} adding new enhancement components to the concept. RESOLVE facilities then produce corresponding \texttt{.h/c} files that provides the application interface implementation of concepts.

@@

### 2014-04-25 tech-project/specify_led.tex
added the smith reference back in and added the relationship diagram.

end LED_Telos_Demo;
\end{verbatim}
%smaller file sizes
%reusable code
%only have to translate a file once
% be able to say that the code we have is the code that was verified.
% our approach takes less ROM. Its not less efficient, it is differently efficient.
Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization. This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}). Note that the enhanced ability of toggling lights is added \textit{on top} of this facility declaration in a similar fashion. The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.

@@

The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase. This signals to the RESOLVE compiler that the user is providing a non-native realization of the \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.

@@

In the terms of embedded systems, these developments are especially as it allows us to write custom low level of the sort required for most embedded applications (e.g. LED strip drivers) while still providing formally specified interfaces that might later form the foundation . It is our hope and intention that new (native) resolve components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstract where we can concern ourselves exclusively with verified, native RESOLVE components.

>>>>

end LED_Telos_Demo;
\end{verbatim}
%smaller file sizes
%reusable code
%only have to translate a file once
% be able to say that the code we have is the code that was verified.
% our approach takes less ROM. Its not less efficient, it is differently efficient.
Prior to using the LED component developed in the previous sections, we first must bind our \texttt{LED\_Template} specification with an appropriate realization. This is accomplished via the facility declaration located directly beneath the \texttt{uses} clause, which pairs the specification (\texttt{LED\_Template}) with a realization (\texttt{Std\_Led\_Realiz}). Note that the ability to toggle is added \textit{on top} of this facility declaration in a similar fashion. The remaining bulk of logic driving the application rests in the non terminating busy loop inside operation \texttt{Main}, where we use our enhancement-provided \texttt{Toggle} operation to successively turn each light within the strip on, then off.

@@

The \texttt{LED\_Telos\_Demo} facility above demonstrates these developments through its use of the ``\texttt{externally realized}" phrase. This signals to the RESOLVE compiler that the user is providing a non-native realization of \texttt{LED\_Template}, with the expectation that it conforms to the specifications dictated in the concept.

@@

In the context of embedded systems, these developments are especially useful as we can now write custom, low level  drivers of the sort required for most embedded applications (e.g. LED strip drivers) while still providing extensible, formally specified interfaces. It is our hope and intention that new (native) RESOLVE components will be layered on top of these low level, externally realized (yet specified) drivers -- eventually reaching a level of abstraction where we can concern ourselves exclusively with verified, native RESOLVE components.
